---
title: "Final"
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: sandstone
      base_font: 
        google: Prompt
      heading_font:
        google: Sen
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: JetBrains Mono
          local: false
---
Figures
======================================================================

Column {data-width=2}
-----------------------------------------------------------------------
### High phenolics diet 
Displayed are the top 25 metabolites exhibiting a high VIP score, influencing the distinction between the purple potato diet and the control diet. The bar graph illustrates the variation in two cytokines detected in the serum of obese animals under these distinct dietary conditions.


```{r setup, include=FALSE}
#install.packages("showtext")
library(knitr)
library(flexdashboard)
library(tidyverse)
library(magrittr)
library(dplyr)
library(ggplot2)
library(htmlwidgets)
library(plotly)
library(forcats)
library(tidyr)
library(ggthemes)
library(ggdark)
library(viridis)
library(readr)
#library(showtext)

```

Column {data-width=5}
-----------------------------------------------------------------------
### Metabolites with higher concentration in liver

```{r, fig.width=100}
liver_vip <- read.csv("Obesedata.csv", header = TRUE)
liver_vip <- liver_vip %>% 
  select(., -1) %>% 
  slice(1:25)

vip_liverOB <- liver_vip %>% 
  mutate(Metabolite = forcats::fct_reorder(Metabolite, VIP.1)) %>% 
  ggplot(aes(x= VIP.1, y= Metabolite, color = Super.Class, text = Sub_Class)) +
  geom_point() +
  labs(x = element_blank(), y = "Metabolites") + 
  scale_fill_viridis_d() +
  dark_theme_bw()

ggplotly(vip_liverOB, tooltip = "text")

```

Column {data-width=5}
-----------------------------------------------------------------------
### immune cell 

```{r}
immunecell <- read.csv("ObeseImmune.csv")

# adding column name to the first and second column 
colnames(immunecell)[1:2] <- c("Genotype", "Diet")

# selecting for two columns
immunecell <- select(immunecell, c(Genotype, Diet, ICAM.1,P.selectin))

# making the data longer
immunecell <- immunecell %>% 
  pivot_longer (cols= (ICAM.1:P.selectin),
                            names_to = "immune_cell", 
                            values_to = "Aboundance") 
immunecell <-immunecell  %>% 
  mutate(Genotype = as.factor(Genotype),
         Diet = as.factor(Diet))

immune_summary = immunecell %>% 
  group_by(Genotype, Diet, immune_cell) %>% 
  summarize(total = sum(Aboundance))

immunecell_plot <- 
  immune_summary %>%  ggplot(aes(x = immune_cell, y = total, 
                               fill = Genotype, color = Diet)) +
  geom_bar(stat = "identity", alpha = 0.9) +
  labs(x = "Immune Cell", y = "Abundance") + 
  scale_fill_viridis_d() +
  dark_theme_bw()


ggplotly(immunecell_plot)

```


High Phenolics diet 
======================================================================  

Column {data-width=4} 
-----------------------------------------------------------------------
The data presented here originates from a preclinical research to investigate how a diet rich in phenolic compounds might influence cardiometabolic health. 
Phenolic compounds are a diverse group of plant-based chemicals known for their potential health-promoting properties.

In this research, both obese and lean mice were subjected to two diets: a standard control diet and a diet supplemented with purple potato (PM), which is likely rich in phenolic compounds. This dietary intervention was carried out over a duration of 11 weeks, allowing sufficient time to see potential effects. 

we used metabolomics to investigate the metabolic change in obese animal when they 
are subjected to two diets, using liquid chromatography-mass spectrometry (LC/MS). 

The dataset labeled "obesedata.csv" contains information about the Variable Importance in Projection (VIP) scores of these liver metabolites. 
VIP scores are indicators used in statistical modeling to identify the most influential variables in distinguishing between different groups or conditions—in this case, potentially highlighting key metabolites affected by the dietary changes.

The "ObeseImmune.csv," presents data obtained through Enzyme-Linked Immunosorbent Assay (ELISA) conducted on the serum (blood) of the obese animals. This analysis specifically focuses on inflammatory cytokines, which are signaling proteins involved in the immune system's response. Notably, these results indicate a reduction in inflammatory cytokine levels among the obese animals that were administered the purple potato diet, suggesting a potential positive effect of this dietary intervention on immune responses associated with obesity.

